### 2014-11-13 tex/bisimulation.tex

In the backward simulation \eqref{eqn:BisimulationBackwards}, for each
$q^\prime$ such that $q \rsym q^\prime$, the proof posits that with any 
$p^\prime$ such that $p^\prime \sqsubset q^\prime$, it is possible to use the
homomorphism in $p^\prime \sqsubset q^\prime$ to derive a $p$ such
that $p \rgse p^\prime$ and $p \in P$.

>>>>

In the backward simulation \eqref{eqn:BisimulationBackwards}, for each
$q^\prime$ such that $q \rsym q^\prime$, the proof posits the existence of some 
$p^\prime$ such that $p^\prime \sqsubset q^\prime$. It then uses the
homomorphism in $p^\prime \sqsubset q^\prime$ to derive a $p$ such
that $p \rgse p^\prime$ and $p \in P$. The existence of $P^\prime$ is established by the existence of $p^\prime$, and $P \sqsubset q$ makes $P^\prime$ the actual successor of $P$.

### 2014-11-13 tex/results.tex
useless commit message

\section{Evaluation}
\label{sec:eval}
In this section we evaluate the effectiveness of the \symtxt{}
approach at analyzing programs with unbounded complex data input in
the context of symbolic execution. In order to perform our evaluation
we implement the \symtxt{} technique and evaluate its efficiacy on
three Java data structure artifacts. We compare the results of the
\symtxt{} approach with other state of the art techniques that
initialize complex data input symbolically.

Symbolic Pathfinder
(SPF)~\cite{visser:ase03,Pasareanu:ISSTA08,pasareanu:ase10,DBLP:journals/ase/PasareanuVBGMR13}. SPF
is an open source engine for performing symbolic execution on Java
bytecode. SPF overwrites the concrete execution semantics of Java
bytecode to generate a symbolic execution tree. SPF contains an
implementation for GSE with lazy initialization. Recent work also
provides implementations of the lazier and lazier\# algorithms in the
SPF framework~\cite{Hillery:2014}.

@@

We create a new extension to SPF in order to implement the~\symtxt{}
approach. In addition to the operations presented in the Javalite
semantics, the implementation contains support for operations over
integers. Examples of bytecode that we overwrite in the SPF engine are
as follows: (i) field access bytecodes, e.g., GETFIELD and ALOAD
bytecodes, to implement the field-access and summarize rules
in~\figref{fig:symInit} and~\figref{fig:fHeap}(a), (ii) the field
write bytecodes, e.g., PUTFIELD and ASTORE bytecodes, to implement the
field-write rules in~\figref{fig:fHeap}(a), (iii) checking equality of
references bytecode, IF\_ACMPEQ and IF\_ACMPNE, to implement the
equals references-true and references-false rules in~\figref{fig:eqs}
(iv) linear arithmetic operations on integers, and (v) comparison
operations on integers. We are currently working on adding support for
floating point operations, arrays, and bit-operations.  We use the
\texttt{jConstraints} library that provides support to handle the heap
constraints~\cite{ase2014-ghilrr,jpf2014-dghirr}. It uses the z3
solver,~\cite{z3}, as the backend to solve the constraints. We
leverage the incremental solving feature in z3 in our experiments. We
also implement other optimizations that cache and re-use solutions to
previous constraints. These optimizations are an important part of our
implementation because only small portions of the heap constraint
changes from one state to another.

@@

\subsection{Case-Study}

The goal of our technique to evaluate the efficiacy of our approach
with respect to other state of the art algorithms for symbolic
execution for dealing for unbounded complex data input. We empirically
evaluate \symtxt{} by considering the following research question:

\begin{description}
\item {\bf RQ1:} How does the cost of using \symtxt{} compare to that
  of \gsetxt{}, lazier, and lazier\# algorithms?

@@

To evaluate we use three Java data structure artifacts (a) Linked List
(b) Binary Search Tree, and (c) Tree Map. These data structures
programs are often used to the evaluate symbolic execution algorithms
with arbitrary heap inputs. The \emph{independent} variable in our
study is the algorithm for initializing symbolic references and the
$k$-bound. The initialization algorithms that we vary in our study
are: \symtxt{}, \gsetxt{}, lazier, and lazier\#. We also vary the
$k$-bound for each the algorithms. Note that $k$-bounding bounds the
length of a reference chain from the root of the heap~\cite{Deng:2006}
We select three dependent variables and measures for our study: (i)
time, (ii) states explored, and (iii) paths generated. The \emph{time}
is the total time taken by each algorithm to explore the symbolic
execution tree as well as total constraint solving time. The
\emph{states explored} represents the number of nodes in the symbolic
execution tree while the \emph{paths generated} represent as the name
suggests the number of unique paths in the symbolic execution tree.

>>>>

\section{Evaluation}
\label{sec:eval}
In this section we evaluate the effectiveness of the \symtxt{}
approach at analyzing programs with unbounded complex input data in
the context of symbolic execution. To perform our evaluation
we implement a prototype of the \symtxt{} technique and evaluate its efficiacy on
three Java data structure artifacts. We compare the results of the
\symtxt{} approach with other state-of-the-art symbolic execution techniques 
that support analysis of program with complex input data types.

Symbolic Pathfinder (SPF) is an open source engine for performing symbolic 
execution on Java 
bytecode~\cite{visser:ase03,Pasareanu:ISSTA08,pasareanu:ase10,DBLP:journals/ase/PasareanuVBGMR13}.
SPF overwrites the concrete execution semantics of Java
bytecode to generate a symbolic execution tree. SPF contains an
implementation for GSE with lazy initialization. Recent work also
provides implementations of the lazier and lazier\# algorithms in the
SPF framework~\cite{Hillery:2014}.

@@

The prototype of  our~\symtxt{} approach is implemented as a new extension to SPF.
In addition to the operations presented in the Javalite
semantics (see \secref{sec:precise}), the implementation contains 
support for operations over
integers. Examples of bytecode implemented in SPF to support \symtxt{} 
algorithm include:
(i) field access bytecodes, e.g., GETFIELD and ALOAD, to implement the 
field-access and summarize rules
in~\figref{fig:symInit} and~\figref{fig:fHeap}(a) respectively, (ii) the field
write bytecodes, e.g., PUTFIELD and ASTORE, to implement the
field-write rules in~\figref{fig:fHeap}(a), and (iii) equality checking of
references bytecodes, IF\_ACMPEQ and IF\_ACMPNE, to implement the
equals references-true and references-false rules in~\figref{fig:eqs}.
We also implement linear arithmetic operations on integers, and integer
comparison operations. We are currently working on adding support for
floating point operations, arrays, and bit-operations.  We use the
\texttt{jConstraints} library which provides support for handling heap
constraints~\cite{ase2014-ghilrr,jpf2014-dghirr}. It uses the z3
solver~\cite{deMouraBjorner08Z3} as the underlying constraint solver. We
leverage the incremental solving feature in z3 in our experiments. We
also implement other optimizations that cache and re-use solutions to
previous constraints. These optimizations are an important part of our
implementation because only small portions of the heap constraint
changes from one state to another.

@@

The goal of our experiment is to evaluate the efficiacy of our approach
with respect to other state-of-the-art techniques for symbolic
execution of programs with unbounded complex data input. We empirically
evaluate the \symtxt{} algorithm by considering the following research question:

\begin{description}
\item {\bf RQ1:} How does the cost of the \symtxt{} algorithm compare with
the \gsetxt{} (lazy), lazier, and lazier\# algorithms?

@@

The evaluation is performed using three Java data structure artifacts 
(a) Linked List,
(b) Binary Search Tree, and (c) Tree Map. 
\sjp{next sentence is bumpy}
These data structure
programs are often used to evaluate symbolic execution algorithms
that analyze software using arbitrary heap inputs. The \emph{independent} variable in our
study is the algorithm for initializing symbolic references and the
$k$-bound. The initialization algorithms that we vary in our study
are: \symtxt{}, \gsetxt{}, lazier, and lazier\#. We also vary the
$k$-bound for each of the algorithms. Note that $k$-bounding bounds the
length of a reference chain from the root of the heap~\cite{Deng:2006}.
We select three dependent variables and measures for our study: (i)
time, (ii) states explored, and (iii) paths generated. The \emph{time}
is the total time taken by each algorithm to explore the symbolic
execution tree as well as total constraint solving time. The
\emph{states explored} represents the number of nodes in the symbolic
execution tree, and the \emph{paths generated} represents 
the number of unique paths in the symbolic execution tree.
